Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-05-31 paper/src/res.tex
Update movie figure in text

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{surfdens.pdf}
  \caption{The surface density projections of the gas and stars over time of the idealized merger simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$ (i.e., the ``bimodal'' simulation). Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot. In each grouping of four, the lower and upper rows show the face-on and edge-on projections, respectively. The left and right columns show the gas and stellar surface densities, respectively. The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length. The colormap for the gas ranges from $10^3$ to $10^7\,\Msun/\pc^2$, while for the stars ranges from $10^2$ to $3\times10^5\,\Msun/\pc^2$. (A movie of this figure is given in \red{TBD}.)}
  \label{fig:projections}
\end{figure*}

>>>>

\begin{figure*}
  \centering

    \gridline{\fig{all_L30/all_L30_frame60.pdf}{0.3\textwidth}{}
              \fig{all_L30/all_L30_frame70.pdf}{0.3\textwidth}{}
              \fig{all_L30/all_L30_frame80.pdf}{0.3\textwidth}{}
              }
    \gridline{\fig{all_L30/all_L30_frame90.pdf}{0.3\textwidth}{}
              \fig{all_L30/all_L30_frame100.pdf}{0.3\textwidth}{}
              \fig{all_L30/all_L30_frame110.pdf}{0.3\textwidth}{}
              }
    \gridline{\fig{all_L30/all_L30_frame120.pdf}{0.3\textwidth}{}
              \fig{all_L30/all_L30_frame200.pdf}{0.3\textwidth}{}
              \fig{all_L30/all_L30_frame320.pdf}{0.3\textwidth}{}
              }
  % \includegraphics[width=\textwidth]{surfdens.pdf}
  \caption{The surface density projections of the gas and stars over time of the idealized merger simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$ (the ``bimodal'' simulation). Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot. In each grouping of four, the lower and upper rows show the face-on and edge-on projections, respectively. The left and right columns show the gas and stellar surface densities, respectively. The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length. The colormap for the gas ranges from $1$ to $10^2\,\Msun/\pc^2$, while for the stars ranges from $1$ to $10^4\,\Msun/\pc^2$. (A movie of this figure is given in \red{TBD}.)}
  \label{fig:projections}
\end{figure*}
